MixEth: efficient trustless coin mixing service for Ethereum

### 2018-11-05 article/main.tex
Testcases for invalid deposit

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
\begin{bbrenv}{A}
 \begin{bbrbox} [name=\bdv]
 \pseudocode {
	 \text{$\textsf{PK}_{B} = (s_{0}C^{*}, s_{1}C^{*})$} \\
	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{l_{b}}})$}
	 }

 \begin{bbrenv}{B}
 \begin{bbrbox}[name=\adv]
 \pseudocode{
 	 \text{Input: $PK_{B}, tx$} \\
	 \text{Output: $b^'$} \\
	 }
 \end{bbrbox}

@@

 \bbrinput{$(s_{0}G,C^{*},s_{b}C^{*})$}
 \bbroutput{$b^'$}
\end{bbrenv}

@@

Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(s_{0}G,C^{*},s_{b}C^{*})$. If original keys are $(s_{0}G, s_{1}G)$ and shuffled keys are $\textsf{PK}_{B}=(s_{0}C^{*}, s_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$. Then a withdrawal transaction occurs from $s_{b}C^{*}$. After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will outpu the very same bit. It is straightforward to see that $\bdv$ wins the DDH-game if and only if $\adv$ wins the $\textsf{G}^{with, anon}_{mix, \adv}$ security game. Therefore, by the assumption that recipient anonymity does not hold we have that $$\textsf{non-negl}(\lambda)=\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\Pr[\textsf{DDH}_{\bdv}],$$ which contradicts to the DDH assumption.

>>>>

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
\begin{bbrenv}{A}
 \begin{bbrbox} [name=\bdv]
 \pseudocode {
 	 \text{$c_{1}\stackrel{\$}{\leftarrow}\mathbb{Z}_p$} \\
	 \text{$\textsf{PK}_{B} = (c_{0}G, c_{1}G)$} \\
	 \text{$b \stackrel{\$}{\leftarrow} \bin $} \\
	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{c_{b}}})$}
	 }

 \begin{bbrenv}{B}
 \begin{bbrbox}[name=\adv]
 \pseudocode{
 	 \text{Input: $PK_{B}, tx$} \\
	 \text{Output: $b^'$}
	 }
 \end{bbrbox}

@@

 \bbrinput{$(sG,cG,c_{0}G)$}
 \bbroutput{$\lnot b\lnot{b^'}+b$}
\end{bbrenv}

@@

Towards contradiction let us assume that the recipient anonymity does not hold. Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(sG,cG,c_{0}G)$. Adversary $\bdv$ generates uniformly random public key $c_{1}G$ and invokes $\adv$ with the set $\textsf{PK}_{B}=(c_{0}C^{*}, c_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$. Then a withdrawal transaction occurs from $c_{b}G$. After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will output $\lnot b^{'}$. If $\adv$ outputs $0$ and $b=b^{'}$, this signals to $\bdv$ that $c_{0}G$ might potentially be of the form $scG=c_{0}G$  i.e. it is a DDH tuple, therefore $\bdv$ outputs $1$. In all the other cases $\bdv$ outputs a random bit. Therefore we have that $\bdv$ has an adventage in their DDH-game if and only if $\adv$ wins their $\textsf{G}^{with, anon}_{mix, \adv}$ security game. Since we assumed that recipient anonymity does not hold we have that $$\Pr[\textsf{DDH}_{\bdv}]=\frac{1}{2}+\frac{1}{2}*\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\frac{1}{2}+\frac{1}{2}*\textsf{non-negl}(\lambda),$$ which contradicts to the DDH assumption.

\section{Proof of Availability}
\section{Proof of Theft Prevention}
